Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Final tweaks

Little et al\. however argued for \emph{probabilistic
interestingness}. Little et al\. proposed a test to test for \emph{probabilistic
interestingness}: a) multiple goal trajectories, b) at least one pair of goal
trajectories that have a common initial sequence and c) there is at least one
goal trajectory that if a action is executed the probability reaching a dead
end decreases.

Replanners surprisingly outperformed other planners in the first IPPC domains,
especially FF-Replan in IPPC-04. The good performance for replanners was
because of the way domains were constructed. Later competitions used FH-MDPs.
\textsc{Gourmand} is a state-of-the-art MDP solver that performed better than
other planners like \textsc{Glutton} or PROST for FH-MDP benchmark domains.

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC\. By looking closely at the domains
we identified some issues with the domains, to make it more difficult for
FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
easier for a replanner in the \textsc{Navigation} domain. The UAV domain seems
to have resemblances of the \textsc{Navigation} domain and the
\textsc{SysAdmin} domain.

>>>>

Little et al.\@ however argued for \emph{probabilistic
interestingness}. Little et al.\@ proposed a test to test for \emph{probabilistic
interestingness}: a) multiple goal trajectories, b) at least one pair of goal
trajectories that have a common initial sequence and c) there is at least one
goal trajectory that if a action is executed the probability reaching a dead
end decreases.

Replanners surprisingly outperformed other planners in the first IPPC domains,
especially replanner FF-Replan in IPPC-04. The good performance for replanners was
because of the way domains were constructed, with no or few dead ends.
Later competitions used FH-MDPs. \textsc{Gourmand} is a state-of-the-art MDP
solver that performed better than other planners like \textsc{Glutton} or PROST
for FH-MDP benchmark domains.

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC\. By looking closely at the domains
we identified some issues with the domains, to make it less interesting for
FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
more interesting for a replanner in the \textsc{Navigation} domain. The UAV
domain seems to have resemblances of the \textsc{Navigation} domain and the
\textsc{SysAdmin} domain.
